Current State of Knowledge Representation Systems for Robotics

### 2011-11-21 paper.tex
Added a Comparison Criteria section: Strategies to deal with physical world
Added 'Interaction with humans' to the Comparison Criteria
Tune column widths of the main table

@@

\begin{itemize}
	\item  Knowledge acquisition possible\ldots{}
	\begin{itemize}
		\item  \ldots{}through interaction? How?
		\item  \ldots{}through the Web? How?
		\item  \ldots{}through learning? How?
		\item  \ldots{}through perception? How?
	\end{itemize}

	\item  Integration with supervision
	\begin{itemize}
		\item  Events
		\item  Relation to task planning
	\end{itemize}

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{lllllll}
\hiderowcolors
{\bf Project} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & Lemaignan (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS Ecology & Daoutis, Coradeshi, Loutfi, Saffiotti (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & OWL-Full, 2nd order logics & & \cite{Daoutis2009} \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

>>>>

\subsection{Strategies to deal with the physical world}

\begin{itemize}
	\item  Knowledge acquisition possible\ldots{}
	\begin{itemize}
		\item  \ldots{}through interaction? How?
		\item  \ldots{}through the Web? How?
		\item  \ldots{}through learning? How?
		\item  \ldots{}through perception? How?
	\end{itemize}
	\item Grounding/anchoring strategies
	\item Ability to automatically create new object instances
	\item Ability to merge modalities
\end{itemize}

@@

\begin{itemize}

	\item  Integration with executive layers
	\begin{itemize}
		\item  Events
		\item  Relation to task planning
	\end{itemize}

	\item Interaction with humans

	Both as developers (KRS as a tool to make robot knowledge explicit to the
	robot designer) and end-users (like natural language processing,...)

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.7cm}p{4cm}lp{2.5cm}p{4cm}lp{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & Tenorth (TU Munich) & & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & Lemaignan (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS Ecology & Daoutis, Coradeshi, Loutfi, Saffiotti (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
 & Kollar, Tellex \\
OMKRF \\
 & Roy, Mavridis \\
 & Wrighteagle \\
 & Vincze \\
 & (Bielfeld) \\
ARMAR & Schmidt-Rohr (Karlsruhe) \\
 & (Saarbrücken) \\
 & Hertzberg (Osnabrück) \\
 & (DFKI Bremen) \\
 (based on {\sc KnowRob} & (JSK) \\
DY-KNOW & Heitnz, Dowerty \\

@@

\subsection{KnowRob}
\label{sect|knowrob}

\subsection{ORO}
\label{sect|oro}
